### 2022-01-21 input/related_work.tex
with the related work

\TODO{Vector routing protocols.} 
Content indexing services in geo-distributed infrastructures allow
\processes to retrieve specific content while leveraging the
advantages of replication. These systems mostly rely on dedicated
location services hosted by possibly remote third-party \processes; but
cutting out the middleman requires that each \process maintains its
own index in a decentralized fashion.

@@

Cutting out the middleman by hosting a location service on each and
every \process improves response time of content retrieval. However,
it still requires every \process to index every live replica as well
as their respective distance in order to rank them.
%% The opposite approach consists in hosting the index directly on the
%% nodes, avoiding any prior request to access a content.
\underline{N}amed \underline{D}ata \underline{N}etworking
(NDN)~\cite{nlsr} broadcasts information about cache updates to all
\nodes in the system. Having the entire knowledge of all the replica
locations along with distance information carried into messages, each
\node easily determine where the closest copy of specific content
resides, without contacting any remote
service. \underline{C}onflict-\underline{f}ree \underline{r}eplicated
\underline{d}atatype (CRDT)~\cite{shapiro2011crdts} for set data
structures could also implement such a location service. \Processes
would eventually have a set of all replicas, assuming eventual
delivery of messages.
\noindent Such solutions imply that every \process receives every
message, which contradicts the principles of Edge infrastructures that
aim at reducing the volume of data passing through the network. On the
opposite, each \process running \NAME only registers its closest
replica. This allows \NAME to use scoped broadcast as a communication
primitive to lock down the traffic generated by content indexing based
on distances.
% Such solutions inherently imply that every node will
% eventually receive all messages, contrary to \NAME.

>>>>

Content indexing services in geo-distributed infrastructures allow
\processes to retrieve specific content while leveraging the
advantages of replication. These systems mostly rely on dedicated
location services hosted by possibly remote third-party \processes; but
cutting out the middleman requires that each \process maintains its
own index in a decentralized fashion.

@@

Cutting out the middleman by hosting a location service on each and
every \process improves response time of content retrieval. However,
it still requires every \process to index every live replica as well
as their respective distance in order to rank them.
%% The opposite approach consists in hosting the index directly on the
%% nodes, avoiding any prior request to access a content.
\underline{N}amed \underline{D}ata \underline{N}etworking
(NDN)~\cite{nlsr} broadcasts information about cache updates to all
\nodes in the system. Having the entire knowledge of all the replica
locations along with distance information carried into messages, each
\node easily determine where the closest copy of specific content
resides, without contacting any remote
service. In a routing context, distance-vector routing protocols such as BGP or OSPF~\cite{ospf} similarly broadcast information to all other nodes to infer a topology map of the network and derive routing tables.
\underline{C}onflict-\underline{f}ree \underline{r}eplicated
\underline{d}atatype (CRDT)~\cite{shapiro2011crdts} for set data
structures could also implement such a location service. \Processes
would eventually have a set of all replicas, assuming eventual
delivery of messages.
\noindent Such solutions imply that every \process receives every
message, which contradicts the principles of Edge infrastructures that
aim at reducing the volume of data passing through the network. On the
opposite, each \process running \NAME only registers its closest
replica. This allows \NAME to use scoped broadcast as a communication
primitive to lock down the traffic generated by content indexing based
on distances.
% Such solutions inherently imply that every node will
% eventually receive all messages, contrary to \NAME.
